---
title: "M12InClass"
author: "Alanna Hazlett"
date: "2024-04-16"
output: html_document
---

```{r}
install.packages(vctrs)
library(vctrs)
library(tidyverse)
```

```{r}
head(mtcars)
```

This is our blank canvas. It expects it to be square.
```{r}
mpg %>% 
  ggplot()
```
Make scatterplot of hwy vs cyl in mpg dataset.
```{r}
mpg %>% 
  ggplot(aes(x=cyl,y=hwy))+
      geom_point()
```
Scatterplots of categorical vs categorical variables are not helpful.
```{r}
mpg %>% 
  ggplot(aes(x=class,y=drv))+
      geom_point()
```
Plot math function sin(x)/x.
```{r}
x<- seq(-6*pi,6*pi,length.out=100)
y<-sin(x)/x
df<-data.frame(x,y)
ggplot(aes(x=x,y=y),data=df)+
  geom_line()
```
Plot speed vs dist for cars dataset.
```{r}
ggplot(aes(x=dist,y=speed),data=cars)+
  geom_point()
```
Create the same plot, but utilize color to distinguish point of dist greater than 80.
```{r}
ggplot(aes(x=dist,y=speed),data=cars)+
  geom_point(mapping=aes(color=dist>80))
```
Flip the colors.
```{r}
ggplot(aes(x=dist,y=speed),data=cars)+
  geom_point(mapping=aes(color=dist>80))+
  scale_color_manual(values=c("blue","red"))
#Another way
#ggplot(aes(x=dist,y=speed),data=cars)+
#geom_point(color=ifelse(cars$dist > 80, "red", "blue"))
```
Add geom_smooth
```{r}
ggplot(aes(x=dist,y=speed),data=cars)+
  geom_point(mapping=aes(color=dist>80))+
  geom_smooth(method=lm)+
  scale_color_manual(values=c("blue","red"))

```
Histogram of speed for cars dataset.
```{r}
cars %>% 
  ggplot(aes(x=speed))+
  geom_histogram()
```
Histogram of distance for cars dataset.
```{r}
cars %>% 
  ggplot(aes(x=dist))+
  geom_histogram(bins=10)
```
Faceted plot of a scatterplot of hwy and cty of the mpg with drv as rows and cyl as cols.
```{r}
mpg %>% 
  ggplot()+
  geom_point(aes(x=hwy,y=cty))+
  facet_grid(drv~cyl)
```





