---
title: "M10InClass"
output: html_document
date: "2024-04-02"
---
Write script that gets the first 10 Fibonacci numbers.
```{r}
fib<- numeric(10)
fib[1] <- fib[2] <- 1
for (i in 3:10) {
  fib[i]<-fib[i-2]+fib[i-1]
}
```
Convert script from before into function that takes argument of the length of the sequence. Return the vector.
```{r}
get_fib<-function(n=10) {
  fib<-numeric(n)
  fib[1]<-fib[2]<-1
  for (i in 3:n){
    fib[i]<-fib[i-2]+fib[i-1]
  }
  return(fib)
}
```

```{r}
get_fib(10)
```

Write function that takes numeric x and returns 1 if between zero and one or else returns 0.
```{r}
interval<-function(x) {
  if (x>= 0 & x<= 1) {
    return(1)
  }
  else {
    return(0)
  }
}
```

```{r}
interval(0.25)
interval(2)
interval(1)
interval(4)
interval(0.66)
```

Extract the first 10 letters in lower case and the last 10 letters in uppercase. Slice and return letters 22-24 in uppeercase.
```{r}
print(head(letters,10))
print(tail(LETTERS,10))
print(LETTERS[22:24])
```

Print Fizz for multiples of 3 and not 5, Buzz for 5 and not 3, and FizzBuzz for 3 and 5.
```{r}
for (num in 1:100) {
    if (num %% 3 == 0 && num %% 5 == 0) {
        print(paste(num,"FizzBuzz"))
    }      
    else if (num %% 3 == 0) {
        print(paste(num,"Buzz"))
    }
    else if (num %% 5 == 0) {
        print(paste(num,"Buzz"))
    }
    else print(paste(num))
}
```
